Paper Consumption in Finland, 1488-1828

### 2016-07-14 inst/examples/20151209-HelsinkiDH.Rmd
paper from km2 to sheets

```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>% group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))

p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Paper consumption") +
     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE)) + 
     xlab("Publication decade") + ylab("Paper (km2)")
print(p)

@@

dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper.consumption.km2, na.rm = T), titles = n())

@@

p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper (km2)")
print(p2)
```

>>>>

```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper) & paper > -0.01)

@@

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>% group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper, na.rm = TRUE))

p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Paper consumption") +
     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE)) + 
     xlab("Publication decade") + ylab("Paper")
print(p)

@@

dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper, na.rm = T), titles = n())

@@

p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper")
print(p2)
```

### 2016-07-14 inst/examples/Paper.Rmd
paper from km2 to sheets

```{r summaryinit, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
df <- readRDS("df.Rds")
dfs <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  group_by(author_name) %>%
  summarise(titles=n()) %>% arrange(desc(titles))
top10.authors <- tail(head(authors,11),10)
df.authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(author_name %in% c(top10.authors$author_name)) %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
df.Turku <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Turku") %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
df.Tukholma <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Stockholm") %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
df.Vaasa <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Vaasa") %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
df.Uppsala <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Uppsala") %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
```

@@

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2 <- ggplot(dfs, aes(y = paper, x = publication_year))
p2 <- p2 + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

@@

```{r paper10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2b <- ggplot(df.authors, aes(y = paper, x = publication_year))
p2b <- p2b + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

@@

```{r paperTurku, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Turku <- ggplot(df.Turku, aes(y = paper, x = publication_year))
p2.Turku <- p2.Turku + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

@@

```{r paperTukholma, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Tukholma <- ggplot(df.Tukholma, aes(y = paper, x = publication_year))
p2.Tukholma <- p2.Tukholma + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

@@

```{r paperVaasa, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Vaasa <- ggplot(df.Vaasa, aes(y = paper, x = publication_year))
p2.Vaasa <- p2.Vaasa + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

@@

```{r paperUppsala, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Uppsala <- ggplot(df.Uppsala, aes(y = paper, x = publication_year))
p2.Uppsala <- p2.Uppsala + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

>>>>

```{r summaryinit, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
df <- readRDS("df.Rds")
dfs <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  group_by(author_name) %>%
  summarise(titles=n()) %>% arrange(desc(titles))
top10.authors <- tail(head(authors,11),10)
df.authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(author_name %in% c(top10.authors$author_name)) %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
df.Turku <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Turku") %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
df.Tukholma <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Stockholm") %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
df.Vaasa <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Vaasa") %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
df.Uppsala <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(publication_place == "Uppsala") %>%
  filter(!is.na(paper) & paper > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper))
```

@@

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2 <- ggplot(dfs, aes(y = paper, x = publication_year))
p2 <- p2 + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")

@@

```{r paper10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2b <- ggplot(df.authors, aes(y = paper, x = publication_year))
p2b <- p2b + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")

@@

```{r paperTurku, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Turku <- ggplot(df.Turku, aes(y = paper, x = publication_year))
p2.Turku <- p2.Turku + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")

@@

```{r paperTukholma, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Tukholma <- ggplot(df.Tukholma, aes(y = paper, x = publication_year))
p2.Tukholma <- p2.Tukholma + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")

@@

```{r paperVaasa, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Vaasa <- ggplot(df.Vaasa, aes(y = paper, x = publication_year))
p2.Vaasa <- p2.Vaasa + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")

@@

```{r paperUppsala, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2.Uppsala <- ggplot(df.Uppsala, aes(y = paper, x = publication_year))
p2.Uppsala <- p2.Uppsala + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption")
